--- 
title: An치lise de Dados em **R** em nivel intermedi치rio. 
author: "Bruno Lucian & Claudia Jakelline"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: 
  bookdown::gitbook:
    config:
      edit : null
      download: null
      search: yes
      sharing:
       facebook: yes
       github: yes
       twitter: yes
       linkedin: yes
       weibo: no
       instapaper: no
       vk: no
      fontsettings:
        theme: spacelab
  bookdown::pdf_book:
    keep_tex: yes
documentclass: book
# bibliography: [book.bib, packages.bib]
# biblio-style: apalike
# link-citations: no
github-repo: brunolucian/cursointermediarioR
description: "Livro texto que acompanha o Curso intermedi치rio de An치lise de Dados em R "
---

# Prerequisites

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
